(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned it's a Working Title.

### 2015-02-23 ms.tex
Updates from ShareLaTeX
More text.

>>>>

\btmtodo{Padova parameters, information}

\btmtodo{Show plot}

The Padova models consistently produce radii which are \btmtodo{VALUE\%} 
larger than those predicted by the Dartmouth models. 
There is some evidence that the Dartmouth models may underpredict 
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}. 
Given that these stars form the majority of our sample, this discrepancy
is perhaps not surprising.

\btmtodo{Then we combine them into one set of stellar properties?}
